---
title: "Product Pricing Algorithm"
author: "Business Science"
date: "3/19/2019"
output:
  html_document:
    df_print: paged
    theme: flatly
  pdf_document: default
params:
  interactive: FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%")
```

```{r}
library(tidyverse)
library(tidyquant)
library(parsnip)
library(plotly)
```

```{r}
# source("../00_scripts/separate_bikes_and_outlier_detection.R")
# source("../00_scripts/plot_product_recommendation.R")
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```

```{r}
models_tbl <- read_rds("../00_models/parsnip_models_tbl.rds")
```

## Problem Statement

Research and Development wants help to determine new product ideas and pricing using existing product line as a benchmark.

## Solution Summary

__TODO: INSERT SOLUTION SUMMARY__


## Gap Analysis

### Bike List

__TODO: INSERT BIKE LIST__

```{r}

```

### Gaps

__TODO: INSERT GAP ANALYSIS SUMMARY AND VISUALIZATION__

```{r, out.height="600px"}

```

\newpage
## Price Prediction

__TODO: INSERT PRICE PREDICTION SUMMARY AND TABLE__

```{r}
# CREATE NEW MODELS
new_over_mountain_trigger <- tibble(
    model = "Trigger Al 1",
    frame_material = "Aluminum",
    category_2 = "Over Mountain",
    model_base = "Trigger",
    model_tier = "Aluminum 1",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_triathalon_slice_tbl <- tibble(
    model = "Slice Al 1",
    frame_material = "Aluminum",
    category_2 = "Triathalon",
    model_base = "Slice",
    model_tier = "Ultegra",
    black      = 0,
    hi_mod     = 0,
    team       = 0,
    red        = 0,
    ultegra    = 0,
    dura_ace   = 0,
    disc       = 0
) 

new_bikes_tbl <- bind_rows(new_over_mountain_trigger, 
                           new_triathalon_slice_tbl)
```

```{r}
# GET XGBOOST MODEL

```

```{r}
# OUTPUT PREDICTIONS IN A TABLE

```


