---
title: "Week 2 Challenge"
author: "Business Science"
date: "12/30/2018"
output:
  pdf_document:
    toc: yes
  html_document:
    code_folding: show
    highlight: tango
    theme: flatly
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE
    )
```

# Challenge Summary

This is a short challenge to begin applying what you are learning to the problem at hand. You will go through a series of questions related to the course project goals: 

1. Coming up with a new product idea, and 

2. Segmenting the customer-base

# Objectives

1. Apply `dplyr` and `tidyr` functions to answer questions related to the course projects. 

2. Gain exposure to `rmarkdown`

# Data

To read the data, make sure that the paths point to the appropriate data sets. Saving the file in the main directory should enable the paths to be detected correctly. 

```{r, message=FALSE, warning=FALSE}
# Load libraries
library(tidyverse)
theme_set(tidyquant::theme_tq())
```

```{r}
# Read bike orderlines data
path_bike_orderlines <- "../00_data/bike_sales/data_wrangled/bike_orderlines.rds"
bike_orderlines_tbl <- read_rds(path_bike_orderlines)

glimpse(bike_orderlines_tbl)
```

```{r}
# Read bikes data
path_bikes <- "../00_data/bike_sales//data_raw/bikes.xlsx"
bikes_tbl <- readxl::read_excel(path_bikes)

glimpse(bikes_tbl)
```

# Questions



## 1. What are the unique categories of products? (Difficulty = Low)

- Begin with `bike_orderlines_tbl`
- Use `distinct()` to evaluate 

Review Primary Product Category (`category_1`).

```{r}
bike_orderlines_tbl %>% 
    distinct(category_1)
```


Review Secondary Product Category (`category_2`).

```{r}
bike_orderlines_tbl %>% 
    distinct(category_2)
```

Review Frame Material (`frame_material`).

```{r}
bike_orderlines_tbl %>% 
    distinct(frame_material)
```


## 2. Which product categories have the most sales? (Difficulty = Medium)

- Select appropriate columns from `bike_orderlines_tbl`
- Group and summarize the data calling the new column `Sales`. Make sure to ungroup. 
- Arrange descending by `Sales`
- Rename column names to `Primary Category`, `Secondary Category`, or `Frame Material` (as appropriate).
- Format the Sales as `dollar()` 

Review Primary Product Category (`category_1`).

```{r}
bike_orderlines_tbl %>% 
    select(contains("category"), frame_material, total_price) %>% 
    group_by(category_1) %>% 
    summarize(Sales = sum(total_price)) %>% 
    ungroup() %>% 
    arrange(desc(Sales)) %>% 
    
    rename(`Primary Category` = category_1) %>% 
    mutate(Sales = scales::dollar(Sales)) %>% 
    
    knitr::kable() 
    
```

Review Secondary Product Category (`category_2`).

```{r}
bike_orderlines_tbl %>% 
    select(contains("category"), frame_material, total_price) %>% 
    group_by(category_2) %>% 
    summarize(Sales = sum(total_price)) %>% 
    ungroup() %>% 
    arrange(desc(Sales)) %>% 
    
    rename(`Second Category` = category_2) %>% 
    mutate(Sales = scales::dollar(Sales)) %>% 
    
    knitr::kable()
    
```


Review Frame Material (`frame_material`).

```{r}
bike_orderlines_tbl %>% 
    select(contains("category"), frame_material, total_price) %>% 
    group_by(frame_material) %>% 
    summarize(Sales = sum(total_price)) %>% 
    ungroup() %>% 
    arrange(desc(Sales)) %>% 
    
    rename(`Frame Material` = frame_material) %>% 
    mutate(Sales = scales::dollar(Sales))
    
```

## 3. Do all combinations primary and secondary bike category contain both Aluminum and Carbon frame materials? (Difficulty = High)

Hint - Use summarized sales values and `spread()` to identify gaps in frame materials. 

- Select `category_1`, `category_2`, `frame_material`, and `total_price`
- Summarize the data using group by, summarize and ungroup. 
- Pivot the frame material and sales column into Alumninum and Carbon
- Fill `NA` values with zeros
- Add a `total_sales` column
- Arrange descending by `total_sales`
- Format all numbers as `dollar()`
- Rename all Columns: Primary Category, Secondary Category, Aluminum, Carbon, Total Sales

```{r}
bike_orderlines_tbl %>% 
    select(contains("category"), frame_material, total_price) %>% 
    group_by(category_1, category_2, frame_material) %>% 
    summarize(Sales = sum(total_price)) %>% 
    ungroup() %>%
    
    spread(key = frame_material, value = Sales, fill = 0) %>% 
    # replace_na(list(Alumnimum = 0, Carbon = 0))
    mutate(`Total Sales` = Aluminum + Carbon) %>% 
    arrange(desc(`Total Sales`)) %>% 
    
    mutate_if(is.numeric, scales::dollar) %>% 
    # mutate(Aluminum      = scales::dollar(Aluminum),
    #        Carbon        = scales::dollar(Carbon),
    #        `Total Sales` = scales::dollar(`Total Sales`)) %>% 
    rename(`Primary Category`   = category_1,
           `Secondary Category` = category_2) 


```





