---
title: "Customer Segmentation"
author: "Business Science"
date: "3/19/2019"
output:
  html_document:
    df_print: paged
    theme: flatly
  pdf_document: default
params:
  interactive: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "100%",
    fig.align = "center")
```

```{r}
library(tidyverse)
library(tidyquant)
library(broom)
library(umap)
library(ggrepel)
library(plotly)
```

```{r}
bike_orderlines_tbl <- read_rds("../00_data/bike_sales/data_wrangled/bike_orderlines.rds")
```

```{r}
# source("../00_scripts/plot_customer_segmentation.R")
```


## Problem Statement

Marketing would like to increase email campaign engagement by segmenting the customer-base using their buying habbits. 

## Solution Summary

__TODO: INSERT ANALYSIS AND HEAT MAP__


## Customer Preferences

### Heat Map

__TODO: INSERT ANALYSIS AND HEAT MAP__

```{r, fig.height=12}
# PLOT CUSTOMER HEAT MAP

```

### Customer Segmentation

__TODO: INSERT ANALYSIS AND HEAT MAP__

```{r, fig.height=5, fig.width=7}
# PLOT CUSTOMER SEGMENTS

```


### Customer Preferences By Segment

__TODO: INSERT ANALYSIS AND HEAT MAP__

```{r, fig.height=8}
# PLOT CUSTOMER BEHAVIOR

```

